---
title: "WKBPLAICE 2024 - ple.27.7e"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plaice (_Pleuronectes platessa_) in Division 7.e (western English Channel) - WKBPLAICE 2024

This repository contains the data preparation for ple.27.7e for the benchmark workshop WKBPLAICE 2024.

## R packages 

The following R packages from CRAN are required to run the assessment:

```{r, eval = FALSE}
icesTAF
ggplot2
tidyr
dplyr
foreach
patchwork
XLConnect

```

They can be installed with:
```{r, eval = FALSE}
### list with required packages
req_pkgs <- c("icesTAF", "ggplot2", "tidyr", "dplyr", "foreach", "patchwork", "XLConnect")
### install/update packages
install.packages(req_pkgs)
```

Furthermore, the following FLR (https://www.flr-project.org, https://github.com/flr) packages are required:
```{r, eval = FALSE}
FLCore
```
They can be installed with
``` {r, eval = FALSE}
install.packages("FLCore", repos = c("https://ices-tools-prod.r-universe.dev", "https://cloud.r-project.org"))
```

## Running the code

The easiest way to run the code is to clone or download this repository, navigate into the repository with R and run:
```{r, eval = FALSE}
### load the icesTAF package
library(icesTAF)
### load data and install R packages
taf.bootstrap()
### run all scripts
source.all()
```
