---
title: "2021_ple.27.7e_assessment"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plaice (_Pleuronectes platessa_) in Division 7.e (western English Channel) - WGCSE 2021

This repository recreates the stock assessment for plaice (_Pleuronectes platessa_) in Division 7.e (western English Channel) in `R` from WGCSE 2020.

## R packages 

The following R packages from CRAN are required to run the assessment:

```{r, eval = FALSE}
icesTAF
icesAdvice
icesSAG
ggplot2
dplyr
reshape
Cairo
tidyr
XML
foreach
doParallel
cowplot
```

They can be installed with:
```{r, eval = FALSE}
### list with required packages
req_pkgs <- c("icesTAF", "icesAdvice", "icesSAG", "ggplot2", "dplyr", "reshape", 
              "Cairo", "tidyr", "XML", "foreach", "doParallel", "cowplot")
### install/update packages
install.packages(req_pkgs)
```

Furthermore, the following FLR (https://www.flr-project.org, https://github.com/flr) packages are required:
```{r, eval = FALSE}
FLCore
FLAssess
FLXSA
FLash
ggplotFL
```
For exact reproducibility, it is recommended to use exactly the same package version as used in the assessment. These FLR package are automatically installed into a local library when running the TAF assessment (see below) or by calling
``` {r, eval = FALSE}
taf.bootstrap()
```
Alternatively, they can be manually installed from GitHub with
``` {r, eval = FALSE}
icesTAF::taf.libPaths() # install packages into local TAF library
devtools::install_github("flr/FLCore", ref = "109858c")
devtools::install_github("flr/FLAssess", INSTALL_opts = "--no-multiarch",
                         ref = "14c7752")
devtools::install_github("flr/FLXSA", INSTALL_opts = "--no-multiarch",
                         ref = "40756e4")
devtools::install_github("flr/FLash", INSTALL_opts = "--no-multiarch",
                         ref = "61cb246")
devtools::install_github("flr/ggplotFL", ref = "07c8564")
```
Please note, on Windows `FLAssess`, `FLXSA` and `FLash` can only be installed and used in the 64-bit version of `R` (previously they only worked on 32-bit).

## Running the assessment

The easiest way to run the assessment is to clone or download this repository, navigate into the repository with R and run:
```{r, eval = FALSE}
### load the icesTAF package
library(icesTAF)
### load data and install R packages
taf.bootstrap()
### run all scripts
sourceAll()
```

This code snippet runs the entire data compilation and assessment and creates the tables and figures presented in the WG report.

## Explore results

To view the results created on the TAF server, browse the [GitHub taf branch](https://github.com/ices-taf/2021_ple.27.7e_assessment/tree/taf).

Assessments results can also be browsed on the [TAF application](https://taf.ices.dk/app/stock#!/2021/ple.27.7e).


## Exploratory analyses

This repository contains code for analyses which are not part of the routine assessment. The scripts for these analyses are not executed when replicating this stockassessment because the links are commented out in [`data.R`](data.R), [`model.R`](model.R) and [`report.R`](report.R) and but can be run manually.

### Discard estimation and assessment

The repository contains code for estimating historical discards (see [`data_6_discards.R`](data_6_discards.R)), an XSA assessment with total catch including discards ([`model_4_discards.R`](model_4_discards.R)) and some outputs ([`report_4_discards.R`](report_4_discards.R)).
Furthermore, [`model_5_discards_EqSim.R`](model_5_discards_EqSim.R) contains code to update the biological reference points for the total catch assessment. Please note, that this approach has not been reviewed and is exploratory only. For running this code, the ICES msy R package is required and can be installed with 
```{r, eval = FALSE}
devtools::install_github("ices-tools-prod/msy")
```

### length-based approach

There is code for comparing the catch length distribution to possible reference points (see [`data_5_length_data.R`](data_5_length_data.R)).

### SPiCT
Exploratory SPiCT assessments are available (see [`model_3_SPiCT.R`](model_3_SPiCT.R) and [`report_3_SPiCT.R`](report_3_SPiCT.R)). 
For running the SPiCT trial assessment, the R package `spict` needs to be installed from GitHub:
```{r, eval = FALSE}
devtools::install_github("mawp/spict/spict", ref = "4e0937b")
```

